Collapsed Cores in Globular Clusters, \\ Gauge-Boson Couplings, and AAS\TeX\ Examples

### 2013-10-07 tex/paper1/paper1.tex
fixed some tex

@@

\section{Floating material and so forth}

>>>>

\section{Results}
\label{sec:results}

@@

\section{Coronal seismology and the effect of background assumptions}
\label{sec:corseis}

\begin{figure}
\epsscale{.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or red noise
  background on the detection of an oscillatory signal for simulated
  time-series.  Plot (a) shows the simulated time-series, generated
  from a power spectrum \protect$P(f)\approx f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
 background .  Plot (c) shows the global wavelet power spectrum for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a red-noise background.\label{fig:comparison}}
\end{figure}

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{vaughan2010}.  Figure
\ref{fig:comparison}(b) shows that the assumption of a white-noise
background and a 95\% confidence level leads to the positive detection
of significant oscillatory power in this time series. Figure
\ref{fig:comparison}(c) shows that the assumption of a red-noise
background with the same confidence level significantly reduces the
area for which a detection may be claimed.  This simulated data, along
with the results of Section \ref{sec:results}, suggest that when
examining the wavelet transforms of time-seris for wave packets, a
background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying red-noise as evidence for an oscillatory
signal.
